---
title: "Titanic"
author: "Ricki Subagya"
date: "12/6/2020"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    df_print: paged
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Importing data train

```{r}
train <- read.csv("data_input/train.csv")
```

# Exploring data

```{r}
str(train)
```


```{r}
train$Pclass <- as.factor(train$Pclass)
train$Sex <- as.factor(train$Sex)
train$Embarked <- as.factor(train$Embarked)
```


```{r}
summary(train)
```

# Most survived passanger by passanger class

```{r}
table(train$Survived, train$Pclass)
```

quick summary : 

* the most survived passenger come from the passenger on **class 1**
* the most not survived passenger come from the passenger on **class 3**

# Most survived passanger by passanger sex/gender

```{r}
table(train$Survived, train$Sex)
```

quick summary : 

* female passenger is the most gender of passenger who survived.

# Most survived passanger by port embarked

```{r}
table(train$Survived, train$Embarked)
```

quick summary : 

* the most survived passenger come from the passenger who embarked from port **S**

* the most not survived passenger come from the passenger who embarked from port **S** too

# number passanger survived

```{r}
surv <- train[train$Survived == "1", ]
nrow(surv)
```
quick summary : 

* there are 342 passenger who survived from accident

```{r}
median(train$Fare)
median(surv$Fare)
```

quick summary :

* passenger who survived had an average fare above average fare all passenger 

```{r}
cor(train$Survived, train$Fare)
```
quick summary : 

* about passenger who survived and fare had a weak positive correlation
